### 2020-12-09 paper/sections/experiment.tex
minor experiment

\begin{figure*}[!t]
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
		\centerline{(a) M6 (Bounding box-based)}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
		\centerline{(b) Duke (Bounding box-based)}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
		\centerline{(c) Multi-Camera Dataset (Bounding box-based)}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/m6_label.pdf}}
		\centerline{(d) M6 (label-based)}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/duke_label.pdf}}
		\centerline{(e) Duke (label-based)}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
		\centerline{(f) Multi-Camera Dataset (label-based) \textcolor{note}{running}}
	\end{minipage}		
	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different metrics on different datasets. Each dot represents the results of running each solution.}
	\label{fig: results}
\end{figure*}

\subsection{Configuration Selection}
\label{subsec: configuration}
We simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2. For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up. In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. We FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model. The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.

@@

We use bounding box-based and label-based metric to evaluate AutoConfigure on M6, Duke, and Multi-Camera Dataset video streams. Figure \ref{fig: results} shows that AutoConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and two accuracy metrics on different datasets. Each magenta dot represents one static configuration solution. These static configuration solutions including some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\}, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\}. Each blue dot represents one AutoConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}. The detailed discussion about differents AutoConfigure solutions is in Section \ref{subsec: different sulutions}. As shown in Figure \ref{fig: results}(a)(d), AutoConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset. As shown in Figure \ref{fig: results}(b)(e), AutoConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 80-90\% of the resources on a Duke dataset. As shown in Figure \ref{fig: results}(c)(f), AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset. In a word, AutoConfigure can improve 10-35\% higher accuracy or save 60-90\% resource consumption.

>>>>

\begin{figure*}[!t]
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
		\centerline{(a) M6 (Bounding box-based)}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
		\centerline{(b) Duke (Bounding box-based)}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
		\centerline{(c) Multi-Camera Dataset (Bounding box-based)}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/m6_label.pdf}}
		\centerline{(d) M6 (label-based)}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/duke_label.pdf}}
		\centerline{(e) Duke (label-based)}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear_label.pdf}}
		\centerline{(f) Multi-Camera Dataset (label-based)}
	\end{minipage}		
	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different metrics on different datasets. Each dot represents the results of running each solution.}
	\label{fig: results}
\end{figure*}

\subsection{Configuration Selection}
\label{subsec: configuration}
We simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2. For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up. In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. We use FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model. The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.

@@

We use bounding box-based and label-based metric to evaluate AutoConfigure on M6, Duke, and Multi-Camera Dataset video streams. Figure \ref{fig: results} shows that AutoConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and two accuracy metrics on different datasets. Each magenta dot represents one static configuration solution. These static configuration solutions include some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\} and so on, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\} and so on. Each blue dot represents one AutoConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}. The detailed discussion about differents AutoConfigure solutions is in Section \ref{subsec: different sulutions}. As shown in Figure \ref{fig: results}(a)(d), AutoConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset. As shown in Figure \ref{fig: results}(b)(e), AutoConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 80-90\% of the resources on a Duke dataset. As shown in Figure \ref{fig: results}(c)(f), AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset. In a word, AutoConfigure can improve 10-35\% higher accuracy or save 60-90\% resource consumption.
